\section{Awards}

\cvitem{2024}{Google research award. \emph{Revisiting Memory Tagging for
Security & Performance}.}

\cvitem{2024}{
% \chref{#}
{
IEEE Micro Top Picks 2024.
}
\emph{Going beyond the Limits of SFI: Flexible and Secure Hardware-Assisted In-Process Isolation with HFI}.}

\cvitem{2024}{
% \chref{#}
{
Honorable mention,
} Intel Hardware Security Academic Award 2024.
\emph{Going beyond the Limits of SFI: Flexible and Secure Hardware-Assisted In-Process Isolation with HFI}.}

\cvitem{2023}{Mozilla research award. \emph{Investigating sandboxing of
JavaScript engines}.}

\cvitem{2023}{
    NSF CCF \# 2327338. Collaborative Research: SaTC: CORE: Medium.
\emph{Refine the Gap: Establishing Safety for Modern Foreign Function Interfaces}.
\$1,200,000 (total), \$300,000 (UT Austin).
}

\cvitem{2023}{
Most engaging speaker, UT Austin Research Topics Seminar (Course CS398T).
}

\cvitem{2023}{
\chref{https://dl.acm.org/doi/10.1145/3582016.3582023}{
Distinguished paper award
} at ASPLOS 2023.
\emph{Going beyond the Limits of SFI: Flexible and Secure Hardware-Assisted In-Process Isolation with HFI}.}

\cvitem{2023}{
\chref{https://www.ieee-security.org/TC/SP2023/program-awards.html}{
Distinguished paper award
} IEEE Symposium on Security and Privacy (S\&P), 2023.
\emph{WaVe: a verifiably secure WebAssembly sandboxing runtime}.}

\cvitem{2023}{Noteworthy Reviewer Award at USENIX Security Symposium 2023.}

\cvitem{2022}{Mozilla research award. \emph{RLBox v2: Extending RLBox for more
performant, ubiquitous sandboxing}.}

% https://secdev.ieee.org/2022/ieee-award-ceremony/
\cvitem{2022}{ Winner, IEEE Cybersecurity Awards for Practice 2022.
\emph{Retrofitting fine grain isolation in the Firefox renderer}.}

\cvitem{2022}{
\chref{https://www.nsa.gov/Press-Room/News-Highlights/Article/Article/2902796/nsa-announces-winners-of-annual-best-scientific-cybersecurity-research-paper-co/}{
Honorable mention,
}
%
NSA Best Scientific Cybersecurity Paper. \emph{Retrofitting fine grain isolation
in the Firefox renderer}. }

\cvitem{2022}{
\chref{https://github.com/bytecodealliance/governance/pull/10}{
Recognized contributor
}
to the Bytecode Alliance's formal verification efforts.
}

\cvitem{2021}{ Google V8 research award. \emph{Practical, portable, and
verified library sandboxing using Wasm}.}

\cvitem{2021}{ Fastly's ``\emph{The edge computer project}'' award. Verifiable
and spectre-safe sandboxing at the edge.}

\cvitem{2021}{
\chref{https://shravanrn.com/csaw-veriwasm-award.pdf}{
Finalist,
}
%
Applied Research Competition, CSAW 2021.
\emph{\foreignlanguage{russian}{Довер\'{я}й, но провер\'{я}й}: {SFI} safety for
native-compiled {Wasm}}.}

\cvitem{2020}{
\chref{https://cse.ucsd.edu/graduate/cse-department-awards}{
Winner,
}
%
Doctoral Award for Excellence in Research, Computer Science and Eng., UC
San Diego.}

\cvitem{2020}{
\chref{https://shravanrn.com/csaw-rlbox-award.pdf}{
Winner,
}
%
Applied Research Competition, CSAW 2020.
\emph{Retrofitting fine grain isolation in the Firefox renderer}.}

\cvitem{2020}{
\chref{https://www.usenix.org/conference/usenixsecurity20/presentation/narayan}{
Distinguished paper award
} at the USENIX Security Symposium 2020.
\emph{Retrofitting fine grain isolation in the Firefox renderer}.}
