\section{Publications}

\mkbib{
%
S. Narayan, T. Garfinkel, E. Johnson, Z. Yedidia, Y. Wang, A. Brown, A.
Vahldiek-Oberwagner, M. LeMay, W. Huang, X. Wang, M. Sun, D. Tullsen, D. Stefan.
%
\chref{https://shravanrn.com/pubs/seguecg.pdf}{
    Segue \& ColorGuard: Optimizing SFI Performance and Scalability on Modern Architectures.
}
%
Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2025.
}

\mkbib{
%
S. Narayan, T. Garfinkel, M. Taram, J. Rudek, D. Moghimi, E. Johnson, C. Fallin,
A. Vahldiek-Oberwagner, M. LeMay, R. Sahita, D. Tullsen, D. Stefan.
%
\chref{https://shravanrn.com/pubs/microtop-hfi.pdf}
{
    Hardware-Assisted Fault Isolation: Going Beyond the Limits of Software-Based Sandboxing.
}
%
\chref{https://www.computer.org/csdl/magazine/mi/2024/04/10589574/1YraIVp37Hy}{IEEE Micro Top Picks, 2024}.
}

\mkbib{
%
S. Narayan, T. Garfinkel, M. Taram, J. Rudek, D. Moghimi, E. Johnson, C. Fallin,
A. Vahldiek-Oberwagner, M. LeMay, R. Sahita, D. Tullsen, D. Stefan.
%
\chref{https://cseweb.ucsd.edu/~dstefan/pubs/narayan:2023:hfi.pdf}{
    Going Beyond the Limits of SFI: Flexible and Secure Hardware-Assisted In-Process Isolation with HFI.
}
%
Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2023.
}

\mkbib{
%
E. Johnson, E. Laufer, Z. Zhao, S. Narayan, S. Savage, D. Stefan, F. Brown.
\chref{https://cseweb.ucsd.edu/~dstefan/pubs/johnson:2023:wave.pdf}{
    WaVe: a verifiably secure WebAssembly sandboxing runtime.
}
%
IEEE Symposium on Security and Privacy (S\&P), 2023.
}

\mkbib{
%
H. Yavarzadeh, M. Taram, S. Narayan, D. Stefan, D. Tullsen.
\chref{https://cseweb.ucsd.edu/~tullsen/halfandhalf.pdf}{
    Half\&Half: Demystifying Intel’s Directional Branch Predictors for Fast, Secure Partitioned Execution.
}
%
IEEE Symposium on Security and Privacy (S\&P), 2023.
}


\mkbib{
%
S. Narayan, T. Garfinkel, E. Johnson, D. Thien, J. Rudek, M. LeMay, A.
Vahldiek-Oberwagner, D. Tullsen, D. Stefan.
%
\chref{https://plas2022.github.io/files/pdf/SegueColorGuard.pdf}{
    Segue \& ColorGuard: Optimizing SFI Performance and Scalability on Modern x86.
}
%
Programming Languages and Analysis for Security (PLAS), 2022.
}

\mkbib{
%
M. Kolosick, S. Narayan, C. Watt, M. LeMay, D. Garg,
R. Jhala, and D. Stefan.
%
\chref{https://popl22.sigplan.org/details/POPL-2022-popl-research-papers/27/Isolation-Without-Taxation-Near-Zero-Cost-Transitions-for-WebAssembly-and-SFI}{
    Isolation without taxation: Near zero cost transitions for SFI.
}
%
Principles of Programming Languages (POPL), 2022.
}

\mkbib
{
%
S. Narayan, C. Disselkoen, and D. Stefan.
%
\chref{https://secdev.ieee.org/2021/program/}{
Tutorial: Using RLBox to sandbox unsafe C code.
}
%
IEEE Secure Development Conference (SecDev), 2021.
}

\mkbib{
%
S. Narayan, C. Disselkoen, D. Moghimi, S. Cauligi, E. Johnson,
Z. Gang, A. Vahldiek-Oberwagner, R. Sahita, H. Shacham, D. Tullsen,
D. Stefan.
%
\chref{https://www.usenix.org/conference/usenixsecurity21/presentation/narayan}{
    Swivel: Hardening WebAssembly against Spectre.
}
%
USENIX Security Symposium, 2021.
}

\mkbib{
%
E. Johnson, Y. Alhessi, D. Thien, S. Narayan, F. Brown,
S. Lerner, T. McMullen, S. Savage, and D. Stefan.
%
\chref{https://www.ndss-symposium.org/wp-content/uploads/ndss2021_5B-3_24078_paper.pdf}{
    \foreignlanguage{russian}{Довер\'{я}й, но провер\'{я}й}: {SFI} safety for native-compiled {Wasm}.
}
%
Network and Distributed System Security Symposium (NDSS), 2021.
}

\mkbib{
%
T. Garfinkel, S. Narayan, C. Disselkoen, H. Shacham, and D. Stefan.
%
\chref{https://www.usenix.org/system/files/login/articles/login_winter20_04_garfinkel-tal.pdf}{
    The road to less trusted code: Lowering the barrier to in-process sandboxing.
}
%
Article in USENIX ;login; journal, Winter 2020.
}

\mkbib{
%
S. Narayan, C. Disselkoen, T. Garfinkel, N. Froyd, E. Rahm,
S. Lerner, H. Shacham, and D. Stefan.
%
\chref{https://www.usenix.org/conference/usenixsecurity20/presentation/narayan}{
    Retrofitting fine grain isolation in the Firefox renderer.
}
%
USENIX Security Symposium, 2020.
}

\mkbib{
%
J. Talpin, J. Marty, S. Narayan, D. Stefan, and R. Gupta.
%
\chref{http://mesl.ucsd.edu/pubs/Talpin_STAMP2019.pdf}{
    Towards verified programming of embedded devices.
}
%
Invited paper at Design, Automation and Test in Europe Conference, 2019.
}


\mkbib{
%
M. Smith, C. Disselkoen, S. Narayan, F. Brown, and D. Stefan.
%
\chref{https://www.usenix.org/conference/woot18/presentation/smith}{
    Browser history re:visited.
}
%
USENIX Workshop on Offensive Technologies (WOOT), 2018.
}

\mkbib{
%
F. Brown, S. Narayan, Riad S. Wahby, Dawson Engler, R. Jhala, and
D. Stefan.
%
\chref{https://www.ieee-security.org/TC/SP2017/papers/16.pdf}{
    Finding and preventing bugs in JavaScript bindings.
}
%
IEEE Symposium on Security and Privacy (S\&P), 2017.
}

