\documentclass[10pt, letterpaper]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
% \usepackage[T1]{fontenc}
\usepackage{gillius}
% sudo apt install cm-super texlive-lang-cyrillic

\usepackage[scale=0.81]{geometry}
\recomputelengths

\newcommand\chref[3][cyan]{\href{#2}{\color{color1}#3}}

\title{}

% \date{\vspace{-1em}}

\pagestyle{plain}

\moderncvtheme[blue]{classic}

\firstname{Shravan Ravi}
\familyname{Narayan}
\renewcommand*{\namefont}{\fontsize{24}{26}\mdseries\upshape}
%\address{4134 4th Ave, Apt 220}{San Diego, 92103}
% \mobile{+1 (425) 209-7454}
\extrainfo{
Assistant Professor \\
University of Texas, Austin \\
\chref{https://shravanrn.com}{https://shravanrn.com}}
\email{shr@cs.utexas.edu}
% \email{shravanrn@gmail.com}

\nopagenumbers{}

\newcounter{bibctr}

\newcommand{\mkbib}[1]{
  \refstepcounter{bibctr}
  \cvitem{\arabic{bibctr}.}{#1}
}

\newcommand{\refbib}[1]{[\ref{bib:#1}]}


\begin{document}
\hypersetup{pdftitle={Shravan Narayan -- CV}}

\maketitle

\section{Education}

\cventry{2022--current}{PostDoc}{University of California, San Diego}
{}{}{Advisor: Prof. Deian Stefan}
%
\cventry{2016--2022}{Ph.D.}{University of California, San Diego}
{}{}{Advisor: Prof. Deian Stefan}
%
\cventry{2009--2013}{B.Eng}{McGill University}{Montreal}{}{}

\section{Publications}

\input{pubs}

\section{Others}

\mkbib{
%
S. Narayan and D. Stefan.
%
\chref{https://blog.sigplan.org/2021/07/27/making-software-sandboxing-practical-using-language-based-techniques/}{
    Making software sandboxing practical using language-based techniques.
}
%
Article in SIGPLAN PL Perspectives blog, Jul 2021.
}


\mkbib{
RLBox: Retrofitting fine grain isolation in the Firefox renderer.
IEEE Symposium on Security and Privacy (S\&P), 2021. Invited poster.}

\mkbib{
S. Narayan, T. Garfinkel, S. Lerner, H. Shacham, and D. Stefan.
\chref{https://arxiv.org/abs/1912.02285}{
    Gobi: WebAssembly as a practical path to library sandboxing.
} In arXiv preprint arXiv:1912.02285, Jan 2019, updated Nov 2019.}

\section{Awards and honors}

\cvitem{2022}{ Winner, IEEE Cybersecurity Awards for Practice, Secure
Development Conference 2022. \emph{Retrofitting fine grain isolation in the
Firefox renderer}.}

\cvitem{2022}{ NSA Best Scientific Cybersecurity Paper, Honorable
Mention. \emph{Retrofitting fine grain isolation in the Firefox renderer}.}

\cvitem{2021}{ Google V8 research award. \emph{Practical, portable, and
verified library sandboxing using Wasm}.}

\cvitem{2021}{ Fastly's ``\emph{The edge computer project}'' award. Verifiable
and spectre-safe sandboxing at the edge.}

\cvitem{2021}{ Finalist, Applied Research Competition, CSAW 2021.
\emph{\foreignlanguage{russian}{Довер\'{я}й, но провер\'{я}й}: {SFI} safety for
native-compiled {Wasm}}.}

\cvitem{2020}{ Doctoral Award for Excellence in Research. Computer Science
and Engineering, UC San Diego.}

\cvitem{2020}{ Winner, Applied Research Competition, CSAW 2020.
\emph{Retrofitting fine grain isolation in the Firefox renderer}.}

\cvitem{2020}{ Distinguished paper award at the USENIX Security Symposium 2020.
\emph{Retrofitting fine grain isolation in the Firefox renderer}.}

\section{Software}

\cvitem{\chref{https://rlbox.dev}{rlbox}}
{A general purpose library sandboxing framework that supports sandboxing plugins.}

\cvitem{\chref{https://github.com/PLSysSec/wasm2c_sandbox_compiler}{sbx-wasm2c}}
{A sandboxing WebAssembly to C compiler for library sandboxing.}

\cvitem{\chref{https://github.com/PLSysSec/veriwasm}{veriwasm}}
{Sandbox validator for Cranelift WebAssembly compiler.}

\cvitem{\chref{https://github.com/PLSysSec/swivel}{swivel}}
{Spectre-resistant WebAssembly compiler.}

\section{Talks}

\cvitem{Sept'22}
{ At the Strange Loop Conference. Don't Get Owned by Your Dependencies: How Firefox Uses In-process Sandboxing To
Protect Itself From Exploitable Libraries. }

\cvitem{Aug'22}
{ At the Black Hat USA Conference. Don't Get Owned by Your Dependencies: How Firefox Uses In-process Sandboxing To
Protect Itself From Exploitable Libraries. }

\cvitem{Oct'21}
{ At the IEEE Secure Development Conference. Using RLBox to sandbox
unsafe C code. }

\cvitem{Aug'21}
{ At the USENIX Security Symposium. Swivel: Hardening WebAssembly against
Spectre. }

\cvitem{Jul'21}
{ At Intel Corp. Swivel: Hardening WebAssembly against Spectre. }

% \cvitem{Oct'20}
% { At MIT's CSAIL Security Seminar. Retrofitting fine grain isolation in the
% Firefox renderer. }

\cvitem{Oct'20}
{ At the Center for Networked Systems' Research Review. RLBox: secure sandboxing for buggy application
components.  }

\cvitem{Aug'20}
{ At the USENIX Security Symposium. Retrofitting fine grain isolation in the
Firefox renderer. }

\cvitem{Jul'20}
{ At Brave Software, Inc. Retrofitting fine grain isolation in the Firefox
renderer. }

\section{Prior work experience}

\cvitem{Jun'21--Sept'21}
%
{{\textbf{Research Intern}, Intel Corp., Portland, OR, USA (Remote).}
%
{\hfill \newline Designed a hardware sandboxing extension based on my research.}}

\cvitem{Jun'20--Sept'20}
%
{{\textbf{Research Intern}, Intel Corp., Portland, OR, USA (Remote).}
%
{\hfill \newline Integrated my sandboxing research with security projects
ongoing at Intel.}}

\cvitem{Oct'13--Aug'16}
%
{{\textbf{Software Development Engineer}, Microsoft Corp., Redmond, WA, USA.}
%
{\hfill \newline Worked in Windows telemetry. Also responsible for developer
tools within our team of 8.}}

\end{document}
