\section{Activities/service}

% Invited to program committee of the USENIX Security Symposium 2025.
% Invited to program committee of the Applied Research Competition, CSAW 2021.

\cvitem{Aug'25--Feb'26}
{ Program committee for the Summer cycle of the ASPLOS Conference 2026. }

\cvitem{Nov'25--Jan'26}
{ ACM India Doctoral Dissertation Award. }

\cvitem{Jan'25--Apr'25}
{ Faculty recruiting committee at UT Austin Computer Science. }

\cvitem{Jan'25--Apr'25}
{ PhD admissions committee at UT Austin Computer Science. }

\cvitem{Mar'25}
{ Reviewer in the Transactions on Dependable and Secure Computing 2025. }

\cvitem{Mar'24--Feb'25}
{ Program committee of the ASPLOS Conference 2025. }

\cvitem{Sep'24}
{ Program committee for Posters at SOSP 2024. }

\cvitem{Sep'24}
{ Program committee of the Applied Research Competition, CSAW 2024. }

\cvitem{Mar'24--May'24}
{ UT Austin
\chref{https://www.cs.utexas.edu/~ans/outreach/curricula.html}{Coding in the Classroom}
outreach to introduce Programming Robots (Lego Mindstorm) to 5th grade students.
}

\cvitem{Jan'24--Apr'24}
{ PhD admissions committee at UT Austin Computer Science. }

\cvitem{Dec'23}
{ UT Austin
\chref{https://www.cs.utexas.edu/~ans/outreach/hour_of_code.html}{Hour of code}
outreach to introduce Programming to K12 students. }

\cvitem{Jun'23--Jun'24}
{ Program committee of the USENIX Security Symposium 2024. }

\cvitem{Aug'23}
{ Program committee of the Kernel Isolation, Safety, and Verification 2023. }

\cvitem{Jun'22--Jun'23}
{ Program committee of the USENIX Security Symposium 2023. }

\cvitem{Nov'22}
{ Program committee of the Programming Languages and Analysis for Security (PLAS), 2022. }

\cvitem{Nov'22}
{ Mentor in \chref{https://grad.ucsd.edu/diversity/programs/grad-amp/index.html}{GradAMP}
graduate application mentorship program at UC San Diego. }

\cvitem{Oct'22}
{ Invited participant in Consumer Reports' Memory safety convening. }

\cvitem{Sep'22}
{ Invited external reviewer on IEEE Symposium on Security and Privacy (S\&P) 2023.}

\cvitem{Aug'22}
{ Program committee of the Applied Research Competition, CSAW 2022. }

\cvitem{Jun'22}
{ Program committee of the IEEE Secure Development Conference 2022. }

\cvitem{Sep'21--May'22}
{ Mentor in \chref{https://ersp.eng.ucsd.edu/}{Early Research Scholars Program
(ERSP)} undergraduate research program at UC San Diego CSE department. }

\cvitem{2019--2021}
{ Student reviewer of papers in IEEE Symposium on Security and Privacy (S\&P)
2019, ACM Symposium on Operating Systems Principles 2019, USENIX Security
Symposium 2020 and 2021. }
