\section{Talks}

\cvitem{May'25}
{ \chref{https://www.qualcomm.com/company/events/product-security-summit\#presentations}{Qualcomm Product Security Summit 2025} (San Diego, CA, USA). The Good, the Bad, and the Ugly: Flexibility \& Performance in ARM MTE.}

\cvitem{Jan'25}
{ Keynote at \chref{https://popl25.sigplan.org/home/waw-2025\#program}{Wasm Workshop 2025 (WAW)
Co-located with POPL} (Denver, CO, USA). Adventures in Making Wasm Fast and More Secure.}

\cvitem{Oct'23}
{ \chref{https://www.cs.cmu.edu/~wasm/wasm-research-day-2023.html}{Wasm
Research Day 2023} (Remote). Optimizing SFI Performance, Scalability, and Spectre
Resistance on Modern CPUs.}

\cvitem{Sept'23}
{ WasmCon 2023 (Bellevue, WA, USA). \chref{https://www.youtube.com/watch?v=r7DZm5tHEeo}{Don't Get
Owned by Dependencies: How Firefox Uses Wasm to Protect Itself from Exploitable
Libraries.}}

\cvitem{Aug'23}
{ At RISC-V Security meeting and RISC-V Runtime Integrity SIG (Remote). Going beyond the
Limits of SFI: Flexible and Secure Hardware-Assisted In-Process Isolation with
HFI. }

\cvitem{June'23}
{ \chref{https://docs.google.com/document/d/1ThtskbjP2-fxgry3Efsatjn_Hyc4GTwcvlawc4PrlMA/edit}{Browser Vulnerability Research Summit 2023} (Remote). RLBox: How Firefox Uses
In-process Sandboxing To Protect Itself From Exploitable Libraries. }

\cvitem{May'23}
{ KTH Royal Institute of Technology's Software Research Meetup (Remote).
Retrofitting fast and secure sandboxing in real systems.
}

\cvitem{Apr'23}
{ At Intel Corp (Remote). Going Beyond the Limits of SFI: Flexible and Secure
Hardware-Assisted In-Process Isolation with HFI. }

\cvitem{Mar'23}
{ ASPLOS 2023 (Canada). Going Beyond the Limits of SFI: Flexible and Secure
Hardware-Assisted In-Process Isolation with HFI. }

\cvitem{Mar'23}
{ Dagstuhl Seminar:
\chref{https://www.dagstuhl.de/en/seminars/seminar-calendar/seminar-details/23101}
{Foundations of WebAssembly} (Germany). Going Beyond the Limits of SFI: Flexible and
Secure Hardware-Assisted In-Process Isolation with HFI. }

\cvitem{Dec'22}
{ Programming Languages and Analysis for Security (PLAS), 2022 (Remote). Segue \&
ColorGuard: Optimizing SFI Performance and Scalability on Modern x86. }

\cvitem{Nov'22}
{ UBC's graduate security class (Remote). Swivel: Hardening WebAssembly against
Spectre. }

\cvitem{Nov'22}
{ CMU's security class (Remote). Retrofitting fast and secure sandboxing in real
systems. }

\cvitem{Sept'22}
{ Strange Loop Conference 2022  (St. Louis, MO, USA).
\chref{https://www.youtube.com/watch?v=23rV-s3DKWM}{
Don't Get Owned by Your Dependencies: How Firefox Uses In-process Sandboxing To
Protect Itself From Exploitable Libraries. }
}

\cvitem{Aug'22}
{ Black Hat USA Conference 2022 (Las Vegas, NV, USA).
\chref{https://www.youtube.com/watch?v=bJ9oWc5cRCI}{
Don't Get Owned by Your Dependencies: How Firefox Uses In-process Sandboxing To
Protect Itself From Exploitable Libraries. }
}

\cvitem{June'22}
{ At UCSD's graduate security class (San Diego, CA, USA). Retrofitting fast and secure sandboxing in
real systems. }

\cvitem{Oct'21}
{ IEEE Secure Development Conference 2021 (Remote). Using RLBox to sandbox unsafe C
code. }

\cvitem{Aug'21}
{ USENIX Security Symposium 2021 (Remote).
\chref{https://www.youtube.com/watch?v=aLAHmnIkg24&feature=emb_imp_woyt}{
    Swivel: Hardening WebAssembly against Spectre.
}}

\cvitem{Jul'21}
{ At Intel Corp (Remote). Swivel: Hardening WebAssembly against Spectre. }

\cvitem{Oct'20}
{ MIT's CSAIL security seminar (Remote). Retrofitting fine grain isolation in the
Firefox renderer. }

\cvitem{Oct'20}
{ At the Center for Networked Systems' Research Review (San Diego, CA, USA).
\chref{https://cns.ucsd.edu/videos/members/CNS-RR-2020/Captioned/2020_10_15_CNS_Narayan.mp4}{
RLBox: secure sandboxing for buggy application components.
}}

\cvitem{Aug'20}
{ USENIX Security Symposium 2020 (Remote).
\chref{https://www.youtube.com/watch?v=3VuZQXbPP9I&feature=emb_imp_woyt}{
Retrofitting fine grain isolation in the Firefox renderer.
}}

\cvitem{Jul'20}
{ At Brave Software, Inc (Remote). Retrofitting fine grain isolation in the Firefox
renderer. }
